Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-17 doc/PRF2022/PRF_main.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The JPs are disks of radius $c$ suspended in a viscous solvent
with center $\aa_i$, and orientation $\theta_i$
relative to the horizontal axis, where $i = 1, \ldots, N_b$ and $N_b$ is
the number of particles. The domain $\Omega \subset \mathbb{R}^2$ is
the solvent phase and $t$ is time. The boundary of $\Omega$ is
$\bd\Omega = \Gamma_1 \cup \cdots \cup \Gamma_{N_b}$, where $\Gamma_i$
is the boundary of Janus particle $i$.
The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
Assuming inertial terms are negligible, the solvent satisfies the Stokes equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
\label{eq:stokesMass}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokesFarfield}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
solvent viscosity. The solvent velocity satisfies the no-slip boundary
condition for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

@@

Letting $\nnu$ be the particle outward normal,
the force $\FF_i$ and torque $T_i$ coming from the free energy
acting on $\Gamma_i$ are~\cite{Fu20}
%from the
%free energy~\cite{Fu20}, we compute the variation of the domain of the
%free energy~\eqref{eq:free_energy} subject
%to~\eqref{eq:SL}--\eqref{eq:SLbc},
%and obtain 
\begin{align}
  \label{eq:FandTdef}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s.
\end{align}
Here,
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right].
\end{align}
is the second-order hydrophobic stress tensor.
Repulsion is rotationally symmetric and
does not enter $T_i$.

@@

The interactions
generated by the HAP-mobility problem formulation
\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly.
In terms of scaling, $\rho$ sets the effective distance of the hydrophobic
interactions; $\rho_0$ determines the distance where attraction and repulsion are in
balance i.e. smaller values of $\rho_0$ lead to more compact particle assemblies.
The rate of self-assembly are proportional to tension $\gamma$,
inversely proportional to viscosity $\mu$, and
approximately inversely proportional to $\rho$~\cite{Fu20}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
We require a method to accurately solve the Stokes and
screened Laplace equations in intricate, unbounded geometries.
We recast~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretize each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc},
we adopt the double layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\eta(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\eta$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \partial \Omega$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \eta(\xx) + \DD[\eta](\xx), \quad
    \xx \in \partial \Omega.
\end{align}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Mobility problem}
%A suspension of $N_b$ Janus particles is immersed in a viscous solvent.
%RJR: In the above sentence, suspection and immersed are redundant 
The JPs are disks of radius $c$ suspended in a viscous solvent with
center $\aa_i$, and orientation $\theta_i$ relative to the horizontal
axis, where $i = 1, \ldots, N_b$, and $N_b$ is the number of particles.
The domain $\Omega \subset \mathbb{R}^2$ is the solvent phase and $t$ is
time. The boundary of $\Omega$ is $\bd\Omega = \Gamma_1 \cup \cdots \cup
\Gamma_{N_b}$, where $\Gamma_i$ is the boundary of Janus particle $i$.
The sets $\Omega$, $\Gamma_1$, \dots, and $\Gamma_{N_b}$ depend on $t$.
Assuming inertial terms are negligible, the solvent satisfies the Stokes
equations
\begin{alignat}{3}
\label{eq:stokes}
  -\mu \Delta \uu + \nabla p &= \mathbf{0}, && \xx \in \Omega, \\
\label{eq:stokesMass}
  \nabla\cdot \uu &= 0, \qquad && \xx \in \Omega, \\
\label{eq:stokesFarfield}
  \uu - \uu_\infty &\to \mathbf{0}, && |\xx| \to \infty,
\end{alignat}
where $\uu$ is the velocity, $p$ is the pressure,
$\uu_\infty$ is the background flow velocity, and $\mu$ is the constant
solvent viscosity. The solvent velocity satisfies the no-slip boundary
condition for a rigid body motion
\begin{align}
  \label{eq:rigid-vel}
  \uu(\xx) = \vv_i + \omega_i (\xx - \aa_i)^\perp, 
    \quad \xx \in \Gamma_i,
\end{align}
where $\vv_i$ is the translational velocity, $\omega_i$ is the angular
velocity, and $\langle x, y \rangle^{\perp} = \langle -y, x\rangle$.

@@

Letting $\nnu$ be the particle outward normal,
the force $\FF_i$ and torque $T_i$ coming from the free energy
acting on $\Gamma_i$ are~\cite{Fu20}
%from the
%free energy~\cite{Fu20}, we compute the variation of the domain of the
%free energy~\eqref{eq:free_energy} subject
%to~\eqref{eq:SL}--\eqref{eq:SLbc},
%and obtain 
\begin{align}
  \label{eq:FandTdef}
  \FF_i = \int_{\Gamma_i} \mathbf{T}\nnu \, \dif s
  - \frac{M}{\rho_0}
  \sum_{j \neq i}
  \frac{\aa_i - \aa_j}{|\aa_i - \aa_j|}
P'\left(\frac{|\aa_i - \aa_j|-2c}{\rho_0}\right)
  ,\quad
T_i = \int_{\Gamma_i} (\xx - \aa_i)^{\perp}\cdot (\mathbf{T}\nnu) \, \dif s.
\end{align}
Here,
\begin{align}
\mathbf{T} = \gamma \left[ \rho^{-1} u^2 \mathbf{I}
  + \rho \left(|\nabla u|^2 \mathbf{I} - 2\nabla u \nabla u^T\right)\right]
\end{align}
is the second-order hydrophobic stress tensor. Repulsion is
rotationally symmetric and does not enter $T_i$.

@@

The interactions generated by the HAP-mobility problem formulation
\eqref{eq:stokes}--\eqref{eq:force} lead to particle self-assembly. In
terms of scaling, $\rho$ sets the effective distance of the hydrophobic
interactions; $\rho_0$ determines the distance where attraction and
repulsion are in balance i.e. smaller values of $\rho_0$ lead to more
compact particle assemblies. The rate of self-assembly is proportional
to tension $\gamma$, inversely proportional to viscosity $\mu$, and
approximately inversely proportional to $\rho$~\cite{Fu20}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Boundary integral representations}
We require a method to accurately solve the Stokes and screened Laplace
equations in intricate, unbounded geometries.  This is done by
recasting~\eqref{eq:stokes}--\eqref{eq:rigid-vel}
and~\eqref{eq:SL}--\eqref{eq:SLbc} as boundary integral equations (BIEs)
and discretizing each BIE at $N$ points on each of the $N_b$ particles
with a collocation method. To express the solution of
\eqref{eq:SL}--\eqref{eq:SLbc}, we adopt the double-layer potential
\begin{align}
\label{eq:SL_BIE}
u({\xx}) = \DD[\sigma](\xx) = \int_{\partial \Omega} 
  \pderiv{G(\xx-\yy)}{\nnu_\yy}\eta(\yy)\, \dif s_\yy, 
  \quad \xx \in \Omega,
\end{align}
where $G(\xx) = \frac{1}{2\pi}K_0(|\xx|/\rho)$ is the fundamental
solution to the screened Laplace equation~\eqref{eq:SL}, $K_0$ is the
zeroth-order modified Bessel function of the second kind, $\nnu_\yy$ is
the unit outward normal at $\yy$, and $\eta$ is a scalar-valued
density function. The subscript in $\dif s_\yy$ denotes integration with
respect to $\yy \in \partial \Omega$. To satisfy the boundary
condition~\eqref{eq:SLbc}, the density function must satisfy\cite{Hsiao2008}
\begin{align}
  \label{eq:SL_BIE2}
  g(\xx) = \frac{1}{2} \eta(\xx) + \DD[\eta](\xx), \quad
    \xx \in \partial \Omega.
\end{align}
